Gaussian mean estimation in simulated data sets

### 2018-12-06 analysis/gauss_shiny_setup.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))

---
title: "Instructions for Interactive plot for exploring results of Gaussian mean estimation experimentsExplore"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

>>>>

---
title: "Instructions for running Shiny server to explore results of Gaussian mean estimation experiments"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

### 2018-12-06 analysis/gaussmeanest.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))

## Set up environment

@@

## Load results

@@

## Simulated data with constant variances

@@

## Simulated data with heteroskedastic errors: "Spikes" mean signal and "Clipped Blocks" variance

@@

## Simulated data with heteroskedastic errors: "Corner" mean signal and "Doppler" variance

>>>>

Set up environment
------------------

@@

Load results
------------

@@

Simulated data with constant variances
--------------------------------------

@@

Simulated data with heteroskedastic errors: "Spikes" mean signal and "Clipped Blocks" variance
----------------------------------------------------------------------------------------------

@@

Simulated data with heteroskedastic errors: "Corner" mean signal and "Doppler" variance
---------------------------------------------------------------------------------------
